---
title: "GBIF dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
```

Introduction
===================================== 

# Exploring the Biogeography of Kelp Forests 

Kelp forests are extensive underwater habitats that range along 25% of the world’scoastlines, providing valuable resources, habitat, and services for coastal communities.
Kelps are useful sentinels of change because they are highly responsive to environmental conditions and have declined across many ecoregions. 

We explore their diversity and biography using an interactive dashboard, which can be used as a template for any other taxa. 

Page 2
===================================== 

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}

```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}

```

### Chart C

```{r}

```

