---
title: "GBIF dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
```

Introduction
===================================== 

#### Exploring the Biogeography of Kelp Forests 

Kelp forests are extensive underwater habitats that range along 25% of the world’scoastlines, providing valuable resources, habitat, and services for coastal communities.
Kelps are useful sentinels of change because they are highly responsive to environmental conditions and have declined across many ecoregions. 

We explore their diversity and biography using an interactive dashboard, which can be used as a template for any other taxa. 

Taxonomy
===================================== 

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}

```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}

```

### Chart C

```{r}

```

Biogeography
=====================================

Help
=====================================
In order to download occurence datasets from Gbif with the provided script, you first have to set up your Gbif account credentials in your R.environ with the following steps:

Set up Gbif credentials in R.environ:
usethis::edit_r_environ()

In the R.environ file, add the following keys and fill in the values with your Gbif account info:
GBIF_USER=""
GBIF_PWD=""
GBIF_EMAIL=""

Then restart R.